Code and information needed to generate the figures needed in 'The influence of small reservoirs on hydrological drought propagation in space and time

### 2023-08-26 R/Figures_code/paper_figures.Rmd
updates after reviews jhydr

```{r, setwd, include = FALSE}
knitr::opts_knit$set(root.dir = "C:/Directory_thesis_codes")
```

```{r, setup, include = FALSE}
setwd("C:/Directory_thesis_codes")
source("./R/Libraries/Libraries.R")
source("./R/Libraries/Libraries_plot.R")
source("./R/Libraries/Functions.R")
source("./R/Libraries/Functions_MC.R")
```

@@

Map of the study area localization on the left. Centralized reservoirs visualization and density representation of the DRN on the right. Made in QGIS utilizing the shapefiles and rasters found in ./Data/DNR and ./Data/Shapefile. The density visualization was made with the QGIS “Density Analysis” plugin. The field NUMPOINTs was then divided by the area of each cell ($25 \hspace{0.1cm} km^2$) to obtain the density ($n°small\hspace{0.1cm}reservoirs/km^2$). The equation used in the new field was: "NUMPOINTS"/($area/1000000) ![Study area framing. North-East Brazil, Ceará and Banabuiú catchment on the left. On the right, centralized reservoirs location and storage capacity, overlayed to DRN's density in the Banabuiú basin.](C:/Directory_thesis_codes/Figures%20and%20tables/paper/Figure_1.png)

@@

![Graphical representation of the Drought Cycle Analysis, from Ribeiro Neto et al. (2022). WSI: Water Scarcity Index, PI: Precipitation Index.](C:/Directory_thesis_codes/Figures%20and%20tables/paper/Figure%202.jpg){width="682"}

@@

```{r figure 5a}
setwd("C:/Directory_thesis_codes")

@@

#Plot
col <- c("Mean precipitation" = "#293462",
         "Sub-basin variation" = "#F24C4C")
p <- ggplot() +
  #Add the droughts rectangles
  # geom_rect(data = date_ranges, aes(xmin = from, xmax = to, ymin = -Inf, ymax = Inf), alpha = 0.4) +
  #Add the sub-basins variation
  geom_ribbon(data = df, aes(x = date, ymin = lowbound, ymax = highbound, fill = "Sub-basin variation"), alpha = 0.5) +
  #Add the mean line
  geom_line(data = df, aes(x = date, y = ma, colour = "Mean precipitation"), size = 1.25) +
  #Add the drought indicator lines
  geom_hline(yintercept = 0, color = 'lightblue', linetype = "dashed", size = 1.25, alpha = 0.8) +
  geom_text(aes(as.Date("1985-01-01"), 0, label = "Normal", vjust = -0.5, hjust = 0), size = 6) +
  geom_hline(yintercept = -1, color = 'yellow', linetype = "dashed", size = 1.25, alpha = 0.8) +
  geom_text(aes(as.Date("1985-01-01"), -1, label = "Moderately dry", vjust = -0.5, hjust = 0), size = 6) +
  geom_hline(yintercept = -1.5, color = 'orange', linetype = "dashed", size = 1.25, alpha = 0.8) +
  geom_text(aes(as.Date("1985-01-01"), -1.5, label = "Severely dry", vjust = -0.5, hjust = 0), size = 6) +
  geom_hline(yintercept = -2, color = 'red', linetype = "dashed", size = 1.25, alpha = 0.8) +
  geom_text(aes(as.Date("1985-01-01"), -2, label = "Extremely dry", vjust = -0.5, hjust = 0), size = 6) +
  #Modify the axis
  scale_y_continuous(name = 'SPI-12', limits = c(-4, 4), breaks = seq(-4, 4, 1)) +
  scale_x_date(name = 'Date', date_breaks = "2 years", date_labels = '%Y', limits = as.Date(c("1980-01-01", "2018-12-01")), expand = c(0,0)) +
  #Add the legend
  scale_color_manual(name = "", values = col) +
  scale_fill_manual(name = "", values = col) +
  theme(
        axis.text.x = element_text(size = 16),
        axis.text.y = element_text(size = 20),
        axis.title = element_text(size = 22),
        legend.title = element_text(size = 20),
        legend.text = element_text(size = 18),
        legend.position = "bottom",
        panel.background = element_rect(fill = "white", colour = "grey50")
        )

@@

plot.save(p, width = 1920, height = 1080, filename = "./Figures and tables/paper/Figure_5.png")
```

>>>>

```{r, setwd, include = FALSE}
knitr::opts_knit$set(root.dir = "C:/DRN-analysis")
```

```{r, setup, include = FALSE}
setwd("C:/DRN-analysis")
source("./R/Libraries/Libraries.R")
source("./R/Libraries/Libraries_plot.R")
source("./R/Libraries/Functions.R")
source("./R/Libraries/Functions_MC.R")
```

@@

Map of the study area localization on the left. Centralized reservoirs visualization and density representation of the DRN on the right. Made in QGIS utilizing the shapefiles and rasters found in ./Data/DNR and ./Data/Shapefile. The density visualization was made with the QGIS “Density Analysis” plugin. The field NUMPOINTs was then divided by the area of each cell ($25 \hspace{0.1cm} km^2$) to obtain the density ($n°small\hspace{0.1cm}reservoirs/km^2$). The equation used in the new field was: "NUMPOINTS"/($area/1000000) ![Study area framing. North-East Brazil, Ceará and Banabuiú catchment on the left. On the right, centralized reservoirs location and storage capacity, overlayed to DRN's density in the Banabuiú basin.](C:/DRN-analysis/Figures and tables/paper/Figure_1.png)

@@

![Graphical representation of the Drought Cycle Analysis, from Ribeiro Neto et al. (2022). WSI: Water Scarcity Index, PI: Precipitation Index.](C:/DRN-analysis/Figures and tables/paper/Figure_2.jpg){width="682"}

@@

```{r figure 5a}
setwd("C:/DRN-analysis")

@@

#Plot
col <- c("Mean precipitation" = "#293462",
         "Sub-basin variation" = "#F24C4C")
p <- ggplot() +
  #Add the droughts rectangles
  # geom_rect(data = date_ranges, aes(xmin = from, xmax = to, ymin = -Inf, ymax = Inf), alpha = 0.4) +
  #Add the sub-basins variation
  geom_ribbon(data = df, aes(x = date, ymin = lowbound, ymax = highbound, fill = "Sub-basin variation"), alpha = 0.5) +
  #Add the mean line
  geom_line(data = df, aes(x = date, y = ma, colour = "Mean precipitation"), size = 1.25) +
  #Add the drought indicator lines
  geom_hline(yintercept = 0, color = 'lightblue', linetype = "dashed", size = 1.25, alpha = 0.8) +
  geom_text(aes(as.Date("1985-01-01"), 0, label = "Normal", vjust = -0.5, hjust = 0), size = 8) +
  geom_hline(yintercept = -1, color = 'yellow', linetype = "dashed", size = 1.25, alpha = 0.8) +
  geom_text(aes(as.Date("1985-01-01"), -1, label = "Moderately dry", vjust = -0.5, hjust = 0), size = 8) +
  geom_hline(yintercept = -1.5, color = 'orange', linetype = "dashed", size = 1.25, alpha = 0.8) +
  geom_text(aes(as.Date("1985-01-01"), -1.5, label = "Severely dry", vjust = -0.5, hjust = 0), size = 8) +
  geom_hline(yintercept = -2, color = 'red', linetype = "dashed", size = 1.25, alpha = 0.8) +
  geom_text(aes(as.Date("1985-01-01"), -2, label = "Extremely dry", vjust = -0.5, hjust = 0), size = 8) +
  #Modify the axis
  scale_y_continuous(name = 'SPI-12', limits = c(-4, 4), breaks = seq(-4, 4, 1)) +
  scale_x_date(name = 'Date', date_breaks = "2 years", date_labels = '%Y', limits = as.Date(c("1980-01-01", "2018-12-01")), expand = c(0,0)) +
  #Add the legend
  scale_color_manual(name = "", values = col) +
  scale_fill_manual(name = "", values = col) +
  theme(
        axis.text.x = element_text(size = 22),
        axis.text.y = element_text(size = 22),
        axis.title.y = element_text(size = 24, face = "bold"),
        axis.title.x = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(size = 22),
        legend.position = "bottom",
        panel.background = element_rect(fill = "white", colour = "grey50")
        )

@@

plot.save(p, width = 1920, height = 1080, filename = "./Figures and tables/paper/Figure_5_new.png")
```
